Large integer arithmetic and polynomial inner product

### 2012-11-14 doc/paper_vli/vli.tex
doc vli

\section*{Polynomial and Inner product definitions}

@@

The choice of the memory layout is important because it facilitates  the usage of the SIMD/AVX instructions. We choose the AoS for the following reasons:
we want reuse the VLI library in other object conception code,  we can not interleave the VLI number with the polynomial like on the figure \ref{AOSSOA}. 
Thus, the data structure will only concern the very large coefficient. For an addition it is a non sense because it does not support carry bit, and less carry bit between entries of the multimedia register, and it  necessitate work under 31 bits to simulate the carry bit. 
The extended multiplication under AVX \texttt{\_\_mm256\_mul\_epu32}  allows only four multiplication of 32 bits, we save a factor two. Nevertheless, on Sandy Bridge, we have 3 ALU, we can not exclude
the execution of several long multiplication in the same time, thus we loose the benefice of the SIMD version. Moreover a large extra work it necessary to prepare the register and shuffle the data into the register which are costly.  To conclude for our range of operations the extended multiplication varies from 128 to 512 bits , a SIMD version will be not optimum. Although, it has been used with success for larger 
integer \cite{SIMD}

>>>>

\section{Art of work}

BLABLABLALBALBALBLALBALBLALBLALBLALBLALBABLALB ALBLALBALBLABLALBLABLALBLA......

\section{Polynomial and Inner product definitions}

@@

The choice of the memory layout is important because it facilitates  the usage of the SIMD/AVX instructions. We choose the AoS for the following reasons:
we want reuse the VLI library in other object conception code,  we can not interleave the VLI number with the polynomial like on the figure \ref{AOSSOA}. 
Thus, the data structure will only concern the very large coefficient. For an addition it is a non sense because it does not support carry bit, and less carry bit between entries of the multimedia register, and it  necessitate work under 31 bits to simulate the carry bit. 
The extended multiplication under AVX \texttt{\_\_mm256\_mul\_epu32}  allows only four multiplication of 32 bits, we save a factor two. Nevertheless, on Sandy Bridge, we have 3 ALU, we can not exclude
the execution of several long multiplication in the same time, thus we loose the benefice of the SIMD version. Moreover a large extra work it necessary to prepare the register and shuffle the data into the register which are costly. For our range of operations the extended multiplication varies from 128 to 512 bits , a SIMD version will be not optimum, although, it has been used with success for larger integer \cite{SIMD}. To conclude, our library is build on AoS format.
